Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-27 paper/paper.qmd

# 使用柱状图展示不同建筑类型的总用电量
ggplot(annual_energy_consumption_data_2021, aes(x = Property_Type, y = `Electricity Use - Grid Purchase (kWh)`, fill = Property_Type)) +
  geom_bar(stat = "identity") +
  ggtitle("Total Electricity Usage by Property Type") +
  xlab("Property Type") +
  ylab("Total Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(b = 45), size = 10),
    axis.text.y = element_blank(), # Remove y-axis numbers
    axis.ticks.y = element_blank(), # Remove y-axis ticks
    axis.text.x = element_text(angle = 65, hjust = 1, size=6),
    legend.key.size = unit(0.3, "cm"),
    legend.text = element_text(size = 5))

>>>>

library(ggplot2)
library(dplyr)

analysis_data <- read.csv("data/analysis_data/analysis_data.csv")

# Reclassify 'Other' types into a single 'Other' category
##analysis_data <- analysis_data %>%
##  mutate(percentage = kWh / sum(kWh) * 100)
analysis_data <- analysis_data %>%
  mutate(Property_Type = case_when(
    grepl("Other", `Primary Property Type - Self Selected`) ~ "Other",
    TRUE ~ `Primary Property Type - Self Selected`
  ))
kWh_count <- analysis_data |>
  group_by(Property_Type)|>
  summarise(kWh = n()) |>
  arrange(desc(kWh))

ggplot(kWh_count, aes(x = Property_Type, y = kWh, fill = Property_Type)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(kWh/sum(kWh) *100 , 1), "%")), vjust=-0.5) +
  ggtitle("Total Electricity Usage by Property Type") +
  xlab("Property Type") +
  ylab("Total Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(b = 45), size = 10),
    axis.text.y = element_blank(), # Remove y-axis numbers
    axis.ticks.y = element_blank(), # Remove y-axis ticks
    axis.text.x = element_text(angle = 65, hjust = 1, size=6),
    legend.key.size = unit(0.3, "cm"),
    legend.text = element_text(size = 5))
